Consistent Polyhedral Surrogates via Embedding

### 2019-05-16 notes/bo-separated.tex
more details, still in progress

Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

@@

\begin{lemma} \label{lemma:U-surject}
  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
  We write $R_U$ for the value of this map at $U$.
\end{lemma}
\begin{proof}
  For each report $r$, write $u_r$ for its embedding point.
  By construciton, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
  Therefore, for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
  By construction, $R_U$ is nonempty because some $r$ is always optimal for any $p$, hence some $u_r \in U$ for all $U \in \mathcal{U}$.
  Furthermore, because $R_U$ are simultaneously optimal when $U$ is, i.e. when $\gamma(p) = U$, we must have that $r \in \Gamma(p) \iff u_r \in U$.
\end{proof}

\begin{lemma} \label{lemma:calibrated-pos}
  If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
\end{lemma}
\begin{proof}
  \bo{TODO, or, this is our proof that a calibrated link is possible!}
\end{proof}

@@

\begin{lemma} \label{lemma:enclose-halfspaces}
  Let $D$ be a closed, convex polyhedron in $\reals^d$.
  For any norm $\|\cdot\|$ and any $\epsilon > 0$, letting $B(D,\epsilon) = \{u : \min_{x \in D} \|u-x\| \leq \epsilon\}$, \bo{or open ball} there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
\end{lemma}
\begin{proof}
  Let $S$ be the $\epsilon$-ball in norm $\|\cdot\|$.
  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
  Now let $S'$ be a ball in $\|\cdot\|_1$ of nonzero radius small enough that $S' \subsetneq S$.
  (Such a ball always exists by equivalence of norms.\bo{cite})
  Because both $D$ and $S'$ are polyhedra, their Minkowski sum $D' = D + S'$ is a polyhedron.\bo{Cite}
  Now, if $T' \subsetneq T$, then for any set $D$, the Minkowksi sum satisfies $D + T' \subsetneq D + T$, so in particular because $\emptyset \subsetneq S' \subsetneq S$, we have
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
  Now we observe that because $D'$ is a polyhedron, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
\end{proof}

>>>>

\bo{Not sure how to integrate this notation into the rest of the document.}

Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space is given.
Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

@@

\begin{lemma} \label{lemma:U-surject}
  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
  We write $R_U$ for the value of this map at $U$.
\end{lemma}
\begin{proof}
  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
  By definition of embedding, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
  So if $U = \gamma(p)$, we must have $R = \Gamma(p)$.
  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
\end{proof}

\begin{lemma} \label{lemma:calibrated-pos}
  If a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
\end{lemma}
\begin{proof}
  \bo{already have this: it is our proof that a calibrated link is possible!}
\end{proof}

@@

\bo{This is embarassing, but I don't have a citation for this lemma so I wrote a hacky, but I think correct, proof.}
\begin{lemma} \label{lemma:open-plus-closed-poly}
  If $D$ is a closed convex polyhedron (the intersection of finitely many closed halfspaces) and $S'$ is an open polyhedron (the intersection of finitely many open halfspaces), then $D+S'$ is an open polyhedron.
\end{lemma}
\begin{proof}
  Let $\bar{D}$ be the closure of $D$ and let $\text{bo}(D)$ be the boundary of $D$.

  By standard results, $D + \bar{S'}$ is a closed polyhedron.
  Furthermore, we claim (1) that $D + S'$ is an open set and (2) that $\bar{D + S'} = D + \bar{S'}$.
  This proves the lemma, because $D+S'$ is the open set whose closure is the closed polyhedron $D + \bar{S'}$.

  To prove (1), let $z \in D + S'$ with $z=x+y, x \in D, y \in S'$.
  Because $S'$ is open, there is some $B(y,\epsilon) \subseteq S'$, so $D+S'$ contains $B(z,\epsilon) = \{x\} + B(y,\epsilon)$, so $z$ is not a boundary point.
  We have shown $D + S'$ does not contain any boundary points, so it is open.

  To prove (2), we must show containment in both directions.
  Let $z \in \bar{D+S'}$.
  If $z$ is in the interior, then $z \in D+S'$, so $z \in D + \bar{S'}$.
  Let $z \in \text{bo}(D+S')$.
  \bo{TODO}
\end{proof}

\begin{lemma} \label{lemma:enclose-halfspaces}
  Let $D$ be a closed, convex polyhedron in $\reals^d$.
  For any $\epsilon > 0$, there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
\end{lemma}
\begin{proof}
  Let $S$ be the standard $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subsetneq S$.
  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.

  Now, if $T' \subsetneq T$, and the sets $T',T,D$ are convex and not equal to the whole of $\reals^d$, then the Minkowksi sum satisfies $D + T' \subsetneq D + T$.
  \bo{TODO - separate into a lemma as well?}
  In particular, because $\emptyset \subsetneq S' \subsetneq S$, we have
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
  Now we observe that because $D'$ is a polyhedron, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
\end{proof}
